---
title: "Stat765Lab03"
output: html_document
date: "2024-03-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task1:

```{r lab03Task1}
# Task 1
set.seed(3047) # replace "765" with your student ID.
n <- 200  
x <- rnorm(n)

residual_std <- exp(x) # error standard deviation is exponential w.r.t. x values

y <- 1.5+3*x + residual_std*rnorm(n)

plot(x, y)

#Task2
fit <- lm(y~x)
summary(fit)

lines(x, (1.7607+3.4102*x), col = 'red')
#Confident interval of the predictions
confint(fit)

sandwich_se = sqrt(diag(vcovHC(fit)))
sandwich_se


coef(fit)-1.96*sandwich_se
coef(fit)+1.96*sandwich_se

z_stat <- coef(fit)/sandwich_se

p_value <- exp(-0.717*z_stat - 0.416*z_stat^2)


```

## describe Task1:

according the plot, with the increasing of x, the y value will spared more from y=1.5+3*x

## Task2:

The standard error of X is  0.1604.

The confident interval is  3.093955 3.726540

The P-Value= <2e-16 *** tells us the significant of the coefficient . the smaller P Value,the more confident we have in the predictions we make with the line.

##Task3:

The Standard Error se(βi^) in SandWich estimator is 0.2448696

the 95% confidence interval for coefficient of X is 2.930303 3.890192

The P-Value is 4.188860e-40 


##Task4:

The confident interval is expended compared to original.

The P-Value is smaller.That means we are more confident with our model.




```{r Lab03Task2}




```
